Long term cloud enhancement events of global solar irradiance over Thessaloniki, Greece

### 2024-06-08 article/article.Rmd
Commit 2024-06-08 08:12

The shortwave solar radiation, reaching Earth's surface, is the main energy source of
the atmosphere and the biosphere, and drives and governs the climate [@Gray2010].  It
has direct practical application; in industries like energy and agricultural
production. The variability of its intensity; can impose difficulties in predicting
the yield; and in designing the specifications of the appropriate equipment.
Significant portion of research has been focused on predicting the renewable energy
production in a fine timescale and in near real-time (for a review see @Inman2013;
@Graabak2016).

@@

On multiple sites, cloud enhancements (CE) have been reported to be able to briefly
exceed the value of the solar constant, resulting of clearness indices above unit. A
summary of extreme enchantment cases (ECE) has been compiled by @Martins2022. There
are also; some practical implications of the cloud enchantments.  The intensity and
duration of enhancements can effect the efficiency and stability of photovoltaic
power production [@Lappalainen2020; @Jaervelae2020]; while ECEs have the potential to
compromise the integrity of photovoltaic plants infrastructure [@DoNascimento2019].
It has also been demonstrated that these events can interfere in the comparison of
ground-based and satellite observations [@Damiani2018].  Global warming has likely
affected cloud coverage in the last few decades. @Liu2023 reported increases in cloud
cover over the tropical and subtropical oceans and decreases over most continents,
while @Dong2023 reported decreases over North America and Europe. To our knowledge,
there is no evidence on whether this trend has affected also the number and strength
of CE events.

<!--
Study of the mechanism has also been done with modeling of different cloud types and
atmospheric conditions.  @Gueymard2017; @Veerman2022
-->
<!--
Instruments respose ....
@Martins2022
-->
Methods of identification of CE events usually include the use of simulated clear
sky irradiance as baseline, that is combined with an appropriate threshold or some
other statistical characteristics, and in some cases, with visual inspection of sky
camera images [@Vamvakas2020; @Mol2023 and references therein].

<!-- our work -->
In this study, we evaluate the effects CE on GHI by investigating their frequency of
occurrence, intensity, and duration in a thirty-year period of GHI observations at
Thessaloniki, Greece.  We used modeled clear sky irradiance, as a baseline to
identify cloud enhancements.  We were able to determine some trends of the
phenomenon, it's Climatology, and some of their  general characteristics. We weren't
able to find a comparable study that provides trends for similar long term dataset,
as ours.  The recording of the GHI signal is the mean of one-minute. Thus, the
minimum resolution of CE events, in this study is one minute.

<!-- Define CE and ECE -->
In the relative bibliography different definition have been used for these events,
some of the are summarized by @Gueymard2017.  Here, we defined as CE
events, the cases when the measured GHI at ground
level, exceeds the expected value under clear-sky conditions.  Similar, we define as
extreme cloud enhancement events (ECE), the cases when GHI, exceeds the Total Solar
Irradiance (TSI) on horizontal plane at ground level.  Although the duration of these
bursts varies, from instantaneous to several minutes, here we are constrained by the
recorded data, to one-minute steps.

@@

## GHI data

>>>>

The shortwave solar radiation, reaching Earth's surface, is the main energy source of
the atmosphere and the biosphere, and drives and governs the climate [@Gray2010].  It
has direct practical application in industries like energy and agricultural
production. The variability of its intensity can impose difficulties in predicting
the yield and in designing the specifications of the appropriate equipment.
Significant portion of research has been focused on predicting the renewable energy
production in a fine timescale and in near real-time (for a review see @Inman2013;
@Graabak2016).

@@

On multiple sites, cloud enhancements (CE) have been reported to be able to briefly
exceed the value of the solar constant, resulting of clearness indices above unit. A
summary of extreme enchantment cases (ECE) has been compiled by @Martins2022. There
are also some practical implications of the cloud enchantments.  The intensity and
duration of enhancements can effect the efficiency and stability of photovoltaic
power production [@Lappalainen2020; @Jaervelae2020] while ECEs have the potential to
compromise the integrity of photovoltaic plants infrastructure [@DoNascimento2019].
It has also been demonstrated that these events can interfere in the comparison of
ground-based and satellite observations [@Damiani2018].  Global warming has likely
affected cloud coverage in the last few decades. @Liu2023 reported increases in cloud
cover over the tropical and subtropical oceans and decreases over most continents,
while @Dong2023 reported decreases over North America and Europe. To our knowledge,
there is no evidence on whether this trend has affected also the number and strength
of CE events.

<!--
Study of the mechanism has also been done with modeling of different cloud types and
atmospheric conditions.  @Gueymard2017; @Veerman2022

Instruments respose ....
@Martins2022
-->

Methods of identification of CE events usually include the use of simulated clear
sky irradiance as baseline, that is combined with an appropriate threshold or some
other statistical characteristics, and in some cases, with visual inspection of sky
camera images [@Vamvakas2020; @Mol2023 and references therein].

<!-- our work -->
In this study, we evaluate the effects CE on GHI by investigating their frequency of
occurrence, intensity, and duration in a thirty-year period of GHI observations at
Thessaloniki, Greece.  We used modeled clear sky irradiance as a baseline to identify
cloud enhancements and we determined long term trends of the above mentioned metrics,
their climatology and some general characteristics.  To our knowledge there are no
other studies that provide trends from such  long dataset.

<!-- Define CE and ECE -->
In the relative bibliography different definition have been used for these events,
some of the are summarized by @Gueymard2017.  Here, we defined as CE
events, the cases when the measured GHI at ground
level, exceeds the expected value under clear-sky conditions.  Similarly, we define as
extreme cloud enhancement events (ECE), the cases when GHI at ground level exceeds the Total Solar
Irradiance (TSI).  Although the duration of these
bursts can vary, from seconds to several minutes, here we are constrained by the
recorded data, to one-minute steps.

@@

## Instrumentation and data

### 2024-06-08 article/article.tex
Commit 2024-06-08 07:13
Commit 2024-06-08 08:12

The shortwave solar radiation, reaching Earth's surface, is the main
energy source of the atmosphere and the biosphere, and drives and
governs the climate \citep{Gray2010}. It has direct practical
application; in industries like energy and agricultural production. The
variability of its intensity; can impose difficulties in predicting the
yield; and in designing the specifications of the appropriate equipment.
Significant portion of research has been focused on predicting the
renewable energy production in a fine timescale and in near real-time
(for a review see \citet{Inman2013}; \citet{Graabak2016}).

@@

On multiple sites, cloud enhancements (CE) have been reported to be able
to briefly exceed the value of the solar constant, resulting of
clearness indices above unit. A summary of extreme enchantment cases
(ECE) has been compiled by \citet{Martins2022}. There are also; some
practical implications of the cloud enchantments. The intensity and
duration of enhancements can effect the efficiency and stability of
photovoltaic power production \citep{Lappalainen2020, Jaervelae2020};
while ECEs have the potential to compromise the integrity of
photovoltaic plants infrastructure \citep{DoNascimento2019}. It has also
been demonstrated that these events can interfere in the comparison of
ground-based and satellite observations \citep{Damiani2018}. Global
warming has likely affected cloud coverage in the last few decades.
\citet{Liu2023} reported increases in cloud cover over the tropical and
subtropical oceans and decreases over most continents, while
\citet{Dong2022} reported decreases over North America and Europe. To
our knowledge, there is no evidence on whether this trend has affected
also the number and strength of CE events.

@@

In this study, we evaluate the effects CE on GHI by investigating their
frequency of occurrence, intensity, and duration in a thirty-year period
of GHI observations at Thessaloniki, Greece. We used modeled clear sky
irradiance, as a baseline to identify cloud enhancements. We were able
to determine some trends of the phenomenon, it's Climatology, and some
of their general characteristics. We weren't able to find a comparable
study that provides trends for similar long term dataset, as ours. The
recording of the GHI signal is the mean of one-minute. Thus, the minimum
resolution of CE events, in this study is one minute.

In the relative bibliography different definition have been used for
these events, some of the are summarized by \citet{Gueymard2017}. Here,
we defined as CE events, the cases when the measured GHI at ground
level, exceeds the expected value under clear-sky conditions. Similar,
we define as extreme cloud enhancement events (ECE), the cases when GHI,
exceeds the Total Solar Irradiance (TSI) on horizontal plane at ground
level. Although the duration of these bursts varies, from instantaneous
to several minutes, here we are constrained by the recorded data, to
one-minute steps.

@@

\hypertarget{ghi-data}{%
\subsection{GHI data}\label{ghi-data}}

>>>>

The shortwave solar radiation, reaching Earth's surface, is the main
energy source of the atmosphere and the biosphere, and drives and
governs the climate \citep{Gray2010}. It has direct practical
application in industries like energy and agricultural production. The
variability of its intensity can impose difficulties in predicting the
yield and in designing the specifications of the appropriate equipment.
Significant portion of research has been focused on predicting the
renewable energy production in a fine timescale and in near real-time
(for a review see \citet{Inman2013}; \citet{Graabak2016}).

@@

On multiple sites, cloud enhancements (CE) have been reported to be able
to briefly exceed the value of the solar constant, resulting of
clearness indices above unit. A summary of extreme enchantment cases
(ECE) has been compiled by \citet{Martins2022}. There are also some
practical implications of the cloud enchantments. The intensity and
duration of enhancements can effect the efficiency and stability of
photovoltaic power production \citep{Lappalainen2020, Jaervelae2020}
while ECEs have the potential to compromise the integrity of
photovoltaic plants infrastructure \citep{DoNascimento2019}. It has also
been demonstrated that these events can interfere in the comparison of
ground-based and satellite observations \citep{Damiani2018}. Global
warming has likely affected cloud coverage in the last few decades.
\citet{Liu2023} reported increases in cloud cover over the tropical and
subtropical oceans and decreases over most continents, while
\citet{Dong2023} reported decreases over North America and Europe. To
our knowledge, there is no evidence on whether this trend has affected
also the number and strength of CE events.

@@

In this study, we evaluate the effects CE on GHI by investigating their
frequency of occurrence, intensity, and duration in a thirty-year period
of GHI observations at Thessaloniki, Greece. We used modeled clear sky
irradiance as a baseline to identify cloud enhancements and we
determined long term trends of the above mentioned metrics, their
climatology and some general characteristics. To our knowledge there are
no other studies that provide trends from such long dataset.

In the relative bibliography different definition have been used for
these events, some of the are summarized by \citet{Gueymard2017}. Here,
we defined as CE events, the cases when the measured GHI at ground
level, exceeds the expected value under clear-sky conditions. Similarly,
we define as extreme cloud enhancement events (ECE), the cases when GHI
at ground level exceeds the Total Solar Irradiance (TSI). Although the
duration of these bursts can vary, from seconds to several minutes, here
we are constrained by the recorded data, to one-minute steps.

@@

\hypertarget{instrumentation-and-data}{%
\subsection{Instrumentation and data}\label{instrumentation-and-data}}
